%% Isaiah Grace
%% May 14 2020

\documentclass[10pt,letterpaper]{article}

% This will be so that we can get a good looking 1st with supertext
\usepackage[super]{nth}

% This is so that we don't print the page number at the bottom
\pagestyle{empty}

% Thanks to this StackExchange answer, we can have a horizontal line under each section
% https://tex.stackexchange.com/questions/84061/how-can-i-make-a-bold-horizontal-rule-under-each-section-title
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\large\bfseries}{\thesection}{1em}{\vspace{-12pt}}[{\vspace{-2pt}\titlerule[0.6pt]}]

\usepackage{changepage}

% I will define a new command to handle each of the entries in the sections below
%\resumeItem
%{Title}
%{Dates}
%{Text}
\newcommand{\resumeItem}[3]{
	\textbf{#1} \hfill #2\\
	\begin{adjustwidth}{15pt}{}
	#3
	\end{adjustwidth}
}

% The geometry specified here will help the text fill the page and reduce the default margins  
\usepackage{geometry}
\geometry{
	voffset=0in,
	hoffset=0in,
	textwidth=7in,
	textheight=10in
	}

\begin{document}
\raggedright
\begin{center}
	\Huge{Isaiah Robert Grace}\\
	\vspace{6pt}
	\large{(617) 901-2132 \hfill github.com/IsaiahGrace \hfill isaiah@graces.com}
\end{center}

\section*{Education}
Purdue University, West Lafayette IN \hfill \textbf{GPA: 3.40}\\
Bachelor of Science in Computer Engineering, Minor in History \hfill Aug 2015 -- Dec 2019

\vspace{2pt}
\textbf{Relevant Coursework:}
Data Structures \& Algorithms,
Computer Architecture,
Microcontrollers,
Object Oriented Programming,
Functional Programming,
Artificial Intelligence,
ASIC design


\section*{Technical Skills}
\begin{tabular*}{\textwidth}{llllll}
	C/C\texttt{++} & Assembly & Java   & Regular Expressions & SystemVerilog    & Cadence synthesis software\\
 	Python         & Bash     & Git    & Questa-Sim          & Linux            & PowerPoint\\
 	\LaTeX         & Matlab   & Scheme & FPGA Synthesis      & Microsoft Office & KiCad PCB Layout\\
\end{tabular*}


\section*{Research and Project Experience}
\resumeItem
{SOCET Research Team, Senior design project}
{Apr -- Dec 2019}
{Coordinated the work of two teammates in creating a custom layout for two logic cells. Specified, documented, and implemented the digital logic design for an APB bus peripheral device. Integrated the team project into the larger System on a Chip for fabrication at MIT Lincoln Labs.}

\resumeItem
{Design and test of MIPS dual core processor}
{Sep -- Dec 2019}
{Designed, tested, implemented, and synthesized a MIPS based processor design featuring a five stage pipeline, and two cores with independent coherent L1 Caches. Used SystemVerilog to implement RTL logic and testbench scripts to validate design. Synthesized design to target an Altera Cyclone FPGA.}

\resumeItem
{Tetris hand-held game console}
{Mar -- May 2019}
{Planned and organized a team of four in developing an STM32 based handheld Tetris console. Created an SPI driver for the embedded display using embedded C++ and assembly.}

\resumeItem
{ASIC Module design for USB to AHB bridge}
{Nov 2018}
{Collaborated to design and test a USB interface module suitable for use on an SoC. Personally designed and wrote SystemVerilog code for the USB receiving/decoding submodule.}

%\resumeItem
%{Zork Text Adventure}
%{Oct 2018}
%{Partnered with another student to create a C++ version of the 1977 Zork text adventure game. Utilized Object Oriented Programming and git version control.}

\resumeItem
{\nth{1} place in Data Structures -- Big Data Challenge}
{Oct 2017}
{Designed and optimized a Huffman encoding algorithm of an arbitrarily large input using a multi-threaded approach. Applied principals of data structures and algorithms to heavily optimize C code. Placed first of 83 students in fasted compression of 64GB of data.}


\section*{Work Experience}
\resumeItem
{Student Researcher: Purdue SOCET team, physical design group}
{Jun -- Aug 2019}
{Developed layout, place and route, and floorplanning workflows using Cadence software for the SOCET System on a Chip physical design}

\resumeItem
{Grader: ECE369 Discrete Mathematics}
{Jan -- May 2019}
{Graded Discrete Mathematics course assignments covering theory of computation, formal logic, graph theory, mathematical induction, state machines, and regular expressions.}

\resumeItem
{Raft Guide: Outdoor Adventure Rafting}
{May -- Aug 2018}
{Guided on class IV-V whitewater. Responsible for customer satisfaction and safety in demanding and dynamic workplace environment. Certified Wilderness First Responder.}

\resumeItem
{Operator: Purdue Rare Isotope Measurement Laboratory}
{Jan 2016 -- May 2018}
{Collected and verified data from Purdue's linear particle accelerator. Operated the accelerator during overnight shifts and responded to emergency shutdowns due to sparking in the accelerator chamber.}


\section*{Leadership}
\resumeItem
{Whitewater Kayaking and Caving Consultant: Purdue Outing Club}
{May 2016 -- Dec 2019}
{Lead and organized caving and whitewater kayaking trips. Ensured safe environment for all participants and practiced inclusive leadership within groups.}

\resumeItem
{Facilitator, participant: EMV sophomore leadership retreat}
{2016, 2017, 2018}
{Participated in, and twice facilitated, a leadership retreat exploring inclusive leadership in the classroom and workplace.}

\resumeItem
{Eagle Scout: BSA}
{2014}
{}


\end{document}